---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting_started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


```

```{r data, message=FALSE, warning=FALSE}

library(MCE)                                               # Load the package
library(dplyr)                                             # Load some data manipulation tools

data.frame(Light = seq(0.001, 1, length = 500)) %>%        # Choose light levels
  mutate("Bright depths" = depth(Light),                   # Calculate depths
         "Shaded depths" = depth(Light, shade = 0.25),     # Calculate depths with shading
         "Shallow community" = shallow(Light),             # Shallow community at these light levels
         "Mesophotic community" = mesophotic(Light),       # Mesophotic community at these light levels
         "Whole reef" = reef(Light)) -> depth.distribution # Calculate reef-wide community values

```


As the default light levels are shared across all the functions, specifying a set of light levels isn't really neccessary. You would get the same result not specifying `Light` anywhere in the above code. I think including it helps to show how things are working, and makes the code more readable. 


The following table show's the values we simulated.


```{r, echo = F}
knitr::kable(depth.distribution[1:5,], format="html") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = T)
```


We don't actually need to go to the effort of simulating a reef to get the boundary depths between the shallow, upper mesophotic, and lower mesophotic zones. `MCE` comes with a built in `reef_boundary` function which returns the **light level** where a patch of reef would look just as much shallow as it does mesophotic.


If we pass this light level to the `depth` function, we can then get the shallowest and deepest depths where the two communities overlap. This is the same as identifying the upper and lower limits of the upper mesophotic zone.


```{r boundaries}

boundaries <- data.frame(Boundary = c("lower", "upper"),
                         Depth = c(depth(reef_boundary()), depth(reef_boundary(), shade = 0.25)))

```

```{r, echo = F}
knitr::kable(boundaries, format="html") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = T)
```

```{r plot, echo=FALSE, fig.align = "center", warning=FALSE, fig.height=1, dpi=800}
library(ggplot2)

ggplot(depth.distribution, aes(y= `Bright depths`, x= `Whole reef`)) + 
  annotate("rect", xmin=-1,xmax=0, ymin=-Inf,
           ymax=Inf, fill="steelblue2", alpha=0.75)+                # Box from -1 to 0
  annotate("rect", xmin=0, xmax=1, ymin=-Inf,
           ymax=Inf, fill="tan2", alpha=0.75)+                      # Box from 0 to 1
  geom_ribbon(data = depth.distribution, aes(ymin = `Shaded depths`, ymax = `Bright depths`, x= `Whole reef`), colour = 
                'white', fill = 'White', alpha = 0.45) +            # Add model range
  geom_point(data = boundaries, aes(x = 0, y = Depth)) +
  labs(y = 'Depth (m)', x = 'Net D value') +  
  coord_cartesian(ylim = c(100, 0), xlim = c(-0.65,0.65), ) +
  annotate("text", label="Shallow", y=93, x=-0.35, col="Black")+
  annotate("text", label="observations", y=100, x=-0.35, col="Black")+
  annotate("text", label="Mesophotic", y=93, x=0.35, col="Black")+
  annotate("text", label="observations", y=100, x=0.35, col="Black")+
  theme_minimal() +                        
  theme(plot.title = element_text(size=12, hjust = 0.5),    
        axis.title.x = element_text(size=10),  
        axis.title.y = element_text(size=10), 
        legend.position = 'bottom') +                              # label sizes and legend position
  NULL
```
